Estimating epidemiological quantities from repeated cross-sectional prevalence measurements

### 2022-03-06 docs/paper.Rmd
use data.table, build pkg docs, switch to using load_all() everywhere
abstract

library(data.table)
library(purrr)
library(here)
library(kableExtra)
## Get tools
functions <- list.files(here("R"), full.names = TRUE)
walk(functions, source)

@@

We used discrete convolutions based to estimate the incidence of infections based on previously published PCR detection curves describing the probability of a positive test as a function of the time since infection.
We further combined time-varying estimates of antibody prevalence with a model of antibody positivity and waning that moved individuals between compartments with or without antibodies based on estimates of new infections, vaccination, probability of seroconversion and waning.

@@

We produced incidence curves of infection describing the UK epidemic from late April 2020 until early 2022.
We used these estimates of incidence to estimate the time-varying growth rate of infections, and combined them with estimates of the generation interval to estimate reproduction numbers.
Biological parameters describing seroconversion and waning, while based on a simple model, were broadly in line with plausible ranges from individual-level studies.

>>>>

library(data.table)
library(purrr)
library(here)
library(kableExtra)
## Get tools
devtools::load_all()

@@

We used a guassian process to model incidence of infections and then estimated observed PCR prevalence by convolving our modelled incidence estimates with a previously published PCR detection curve describing the probability of a positive test as a function of the time since infection. We refined our incidence estimates using time-varying estimates of antibody prevalence combined with a model of antibody positivity and waning that moved individuals between compartments with or without antibodies based on estimates of new infections, vaccination, probability of seroconversion and waning.

@@

We produced incidence curves of infection describing the UK epidemic from late April 2020 until early 2022.
We used these estimates of incidence to estimate the time-varying growth rate of infections, and combined them with estimates of the generation interval to estimate time-varying reproduction numbers.
Biological parameters describing seroconversion and waning, while based on a simple model, were broadly in line with plausible ranges from individual-level studies.
